We need to beat namespotting, no idea how

### 2023-01-16 paperSubmission/paperSubmission1.tex
implemented Patrycja's comments

\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{todonotes}

@@

We analyzed the data from three perspectives: we used the daily data to
(1) build seven time series models estimating the impact of individual
interventions at lags 1-7 days, and (2) to study the impact of the
cumulative number of total interventions received as the experiment
progressed, and (3) we used aggregated data to run a long term
before-and after analysis, comparing the summarized aggression levels
before and after the intervention period.

@@

First, we inspect correlations between predictors to avoid multicolinearity, as highly correlated predictors do not improve predictive performance and artificially inflate uncertainty in their corresponding coefficients in the models. We then develop
a plausible causal model of the situation (Figure
\ref{fig:correlations}). It turns out that to avoid multicolinearity we
cannot condition on CDS if we condition on CAS or CBS. Similarly, for
the time series data, since activity levels in particular day slices are
correlated, it will not be useful to condition on more than one
auto-regressive element (and since the predictive power is the highest
for lag 1 with no discoverable weekly patterns, we will not go further
than lag 1).

To choose the right variables to condition (or not condition) on to
identify the causal effect of the interventions, we need to think about
the causal structure of the problem. Comments during (the intervention period) impact attacks
during, which trigger interventions. Unmeasured user features cause
comments before (the intervention period), which impact attacks before directly. Comments during
(their impact on ADS is already included) impact attacks during directly
and comments after, which impact attacks after and attacks after
directly. Intervention count impacts attacks after and comments after.
The same directions of impact are included for intervention type.
Finally, comments through time are connected causally, and so are
attacks. The structure for the time series data is analogous, except now
instead of before and after, we have multiple daily indices.

@@

Finally, in the before-and-after analysis, we put aside the time series
element, look at aggregated counts before and after the treatment
period, thus obtaining a more of a long-term effect analysis. Moreover,
this time we standardize counts, obtaining continuous variables and
employing normal distribution in the likelihoods, thus also making sure
the overall results are robust under a spectrum of modeling choices. We
build and compared multiple additive models where the outcome variable
is normally distributed around the predicted mean, which is a linear
function of predictors (possibly with interactions). Our general criteria
led to the model whose specification is as follows (we also selected
regularizing prior parameters using prior predictive checks to avoid
unreasonably narrow overall prior distributions, see the appendix for a longer explanation):

@@

That is, we take the resulting mean to be the result of the general
average (\(\alpha\)) and the impact of the following coefficients:
group-specific coefficient for \textsf{ADS}, group coefficient,
group-specific coefficient for \textsf{IC}, interaction coefficient for
\textsf{ADS} and \textsf{IC}, and group-specific coefficient for
\textsf{CBS}. This is plausible \emph{prima facie}, as which group a
user belongs to might have impact on how the number of attacks during
the treatment are related to the number of attacks after, the role of
the intervention count, and the role of comments before. Moreover, the
levels of aggressive behavior displayed by the user during treatment
might have impact on the role played by the intervention count.

@@

\begin{center}\includegraphics[width=1\linewidth]{ figures/fig:dailyResultsPlot-1} \end{center}
\caption{Impact of interventions received lag $1\leq k \leq 7$ on attacks on a given day. High-level coefficients are pictured in black.}
\label{fig:dailyResults}
\end{figure}

@@

let us elaborate on how we decided to use to the seemingly fairly
complicated model we already described in the body of the paper. Once preliminary causal considerations guided our
restrictions on variable selection, we proceed by building models of
increasing complexity, and comparing them in terms of Widely Acceptable
Information Criterion (which we have already discussed). The models
differ mostly in the underlying linear formulae. For computational ease
we will here use quadratic approximations, while in the final analysis
we will deploy Hamiltionian Monte Carlo. The names are meant to decode
the model structure: the predictors are listed before dashes, whereas
interactions are listed after dashes. The comparison results are in
Table \ref{tab:comparison} and plotted in Figure
\ref{fig:modelComparisonPlot}. Notice that there are ways of building a
complicated models that do not result in improvement, as they rather
lead to expected performance lower than that of the null model.

>>>>

\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{todonotes}
\usepackage{rotating}

@@

We analyzed the data from three perspectives: we used the daily data to
(1) build seven time series models estimating the impact of individual
interventions at lags 1-7 days, and (2) to study the impact of the
cumulative number of  interventions received as the experiment
progressed, and (3) we used aggregated data to run a long term
before-and after analysis, comparing the summarized aggression levels
before and after the intervention period.

@@

First, we inspect correlations between predictors to avoid multicolinearity, as highly correlated predictors do not improve predictive performance and artificially inflate uncertainty in their corresponding coefficients in the models. We then develop
a plausible causal model of the situation (Figure
\ref{fig:correlations}). It turns out that to avoid multicolinearity we
cannot condition on CDS (comments during, standardized) if we condition on CAS (comments after, standardized) or CBS (comments before, standardized). Similarly, for
the time series data, since activity levels in particular day slices are
correlated, it will not be useful to condition on more than one
auto-regressive element (and since the predictive power is the highest
for lag 1 with no discoverable weekly patterns, we will not go further
than lag 1).

To choose the right variables to condition (or not condition) on to
identify the causal effect of the interventions, we need to think about
the causal structure of the problem. Comments during (the intervention period) impact attacks
during, which trigger interventions. Unmeasured user features cause
comments before (the intervention period), which impact attacks before directly. Comments during
(their impact on ADS is already included) impact attacks during directly
and comments after, which impact attacks after
directly. Intervention count impacts attacks after and comments after.
The same directions of impact are included for intervention type.
Finally, comments through time are connected causally, and so are
attacks. The structure for the time series data is analogous, except now
instead of before and after, we have multiple daily indices.

@@

Finally, in the before-and-after analysis, we put aside the time series
element, and look at aggregated counts before and after the treatment
period, thus obtaining a more of a long-term effect analysis. Moreover,
this time we standardize counts, obtaining continuous variables and
employing normal distribution in the likelihoods, thus also making sure
the overall results are robust under a spectrum of modeling choices. We
build and compared multiple additive models where the outcome variable
is normally distributed around the predicted mean, which is a linear
function of predictors (possibly with interactions). Our general criteria
led to the model whose specification is as follows (we also selected
regularizing prior parameters using prior predictive checks to avoid
unreasonably narrow overall prior distributions, see the appendix for a longer explanation):

@@

That is, we take the resulting mean to be the result of the general
average (\(\alpha\)) and the impact of the following coefficients:
group-specific coefficient for \textsf{ADS}, group coefficient,
group-specific coefficient for \textsf{IC}, interaction coefficient for
\textsf{ADS} and \textsf{IC}, and group-specific coefficient for
\textsf{CBS}. This is plausible \emph{prima facie}, as which group a
user belongs to might have an impact on how the number of attacks during
the treatment is related to the number of attacks after, the role of
the intervention count, and the role of comments before. Moreover, the
levels of aggressive behavior displayed by the user during treatment
might have an impact on the role played by the intervention count.

@@

\begin{sidewaysfigure}

\begin{center}\includegraphics[width=1\linewidth]{ figures/fig:dailyResultsPlot-1} \end{center}
\caption{Impact of interventions received lag $1\leq k \leq 7$ on attacks on a given day. High-level coefficients are pictured in black.}
\label{fig:dailyResults}
\end{sidewaysfigure}

@@

Let us elaborate on how we decided to use  the seemingly fairly
complicated model we already described in the body of the paper. Once preliminary causal considerations guided our
restrictions on variable selection, we proceed by building models of
increasing complexity, and comparing them in terms of Widely Acceptable
Information Criterion (which we have already discussed). The models
differ mostly in the underlying linear formulae. For computational ease
we will here use quadratic approximations, while in the final analysis
we will deploy Hamiltionian Monte Carlo. The names are meant to decode
the model structure: the predictors are listed before dashes, whereas
interactions are listed after dashes. The comparison results are in
Table \ref{tab:comparison} and plotted in Figure
\ref{fig:modelComparisonPlot}. Notice that there are ways of building a
complicated models that do not result in improvement, as they rather
lead to expected performance lower than that of the null model.
